### 2017-12-24 DASFAA_2018/Gruba/06-perf.tex

In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.

@@

With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
Particularly, for the Feature Extraction module, for practical reasons, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
For the User Cluster module, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
For the Behavior Modeling module, the recent 30 days microblogs of users are used for their short-term interest analysis,
and popular words in the latest 24 hours are returned by Ring as the Hot Event keywords \cite{IEEEexample:ring}.

@@

\stitle{Exp-1: Feature Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

\begin{figure}[tb!]
\centering
\includegraphics[width=.7\linewidth]{figures/Interests}
\caption{Testing Results with Various $\alpha$.}
\label{fig:fe}
\vspace{-1ex}
\end{figure}

\begin{figure}[tb!]
\centering
\includegraphics[width=.85\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets.}
\label{fig:uc}
\vspace{-2ex}
\end{figure}

\begin{figure*}[tb!]
  \centering
  \subfigure[Precision]{
    \label{fig:10-a}
    \includegraphics[width=0.32\textwidth]{figures/precision.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:10-b}
    \includegraphics[width=0.32\textwidth]{figures/recall.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:10-c}
    \includegraphics[width=0.32\textwidth]{figures/F-Measure.eps}}
  \caption{Performance of \sys{} Versus LRC-BQ.}
  \label{fig:10}
\end{figure*}

\stitle{Exp-3: Behavior Modeling}
%
Fig.\ \ref{fig:10} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We evaluate the performance using the metrics of precision, recall, and $F_1$ score.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
The results show that:
%\begin{itemize}

@@

	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
%\end{itemize}

Fig.\ \ref{fig:11} explores the performance of \sys{} when using alternative data items for modeling.
By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
How about using other combinations of the above item(s)?
As shown in Fig.\ \ref{fig:11}, the default setting wins in most cases.

\begin{figure*}
  \centering
  \subfigure[Precision]{
    \label{fig:11-a}
    \includegraphics[width=0.32\textwidth]{figures/precisionofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:11-b}
    \includegraphics[width=0.32\textwidth]{figures/recallofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:11-c}
    \includegraphics[width=0.32\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
  \caption{\sys{} Performance of Using Various Data Items for Modeling.}
  \label{fig:11}
  \vspace{-1ex}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure*}

>>>>

\par In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.

@@

With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
Particularly, for the Feature Extraction module, for practical reasons, we employed a smaller testing dataset (with manually labeled topics for yardstick) to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature};
For the User Cluster module, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
For the Behavior Modeling module, the recent 30 days microblogs of users are used for their short-term interest analysis,
and popular words in the latest 24 hours are returned by Ring as the Hot Event keywords \cite{IEEEexample:ring}.

@@

\stitle{Exp-1: Interest Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
We report the interest accuracy with various $\alpha$ values. Suppose that the label set manually labeled for each microblog is $A$, the label set that our method labeled is $B$. The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.

System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:10-c} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

%\begin{figure}[tb!]
%  \centering
%  \subfigure[Tests with Various $\alpha$.]{
%    \label{fig:fe}
%\includegraphics[width=.355\linewidth]{figures/Interests}}
%  \hspace{0.5in}
%   \subfigure[Silhouette Coefficient Tests.]{
%    \label{fig:10-c}
%  \includegraphics[width=.355\linewidth]{figures/clustering}}
%  \caption{Performance of \sys{} Versus LRC-BQ.}
%    \label{fig:fig-1}
%\end{figure}

\begin{figure}[tb!]
\centering
\begin{minipage}{.5\textwidth}
  \centering
\includegraphics[width=.85\linewidth]{figures/Interests}
\caption{Interest Extraction: Varying $\alpha$.}
\label{fig:fe}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
\includegraphics[width=.8\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Tests.}
\label{fig:10-c} 
\end{minipage}
\end{figure}

\begin{figure*}[tb!]
%\centering
  \subfigure[\sys{} Vs. LRC-BQ]{
    \label{fig:10-a}
    %\vspace{2ex}
    \includegraphics[width=0.5\textwidth]{figures/precision-1.eps}}
 % \hspace{0.5in}
   \subfigure[Varying Items]{
   %\vspace{2ex}
    \label{fig:11-a}
  \includegraphics[width=0.5\textwidth]{figures/precisionofdifferentfeatures.eps}}
  %\vspace{-1ex}
  \caption{Accuracy Evaluation.}
  \label{fig:fig-2}
  \vspace{-4ex}
\end{figure*}

\begin{comment}
\begin{figure*}[tb!]
  \centering
  \subfigure[Precision]{
    \label{fig:10-a}
    \includegraphics[width=0.315\textwidth]{figures/precision.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:10-b}
    \includegraphics[width=0.315\textwidth]{figures/recall.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:10-c}
    \includegraphics[width=0.315\textwidth]{figures/F-Measure.eps}}
  \caption{Performance of \sys{} Versus LRC-BQ.}
  \label{fig:10}
\vspace{-4ex}
\end{figure*}
\end{comment}

\stitle{Exp-3: Behavior Modeling}
%
Fig.\ \ref{fig:10-a} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We evaluate the performance using the metrics of accuracy.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
The results show that:
%\begin{itemize}

@@

	\stab(2) For \sys{}, having user clustering is better than the alternative single group. Ditto for LRC-BQ.
%\end{itemize}

Fig.\ \ref{fig:11-a} explores the performance of \sys{} when using alternative data items for modeling.
By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
%How about using other combinations of the above item(s)?
As shown in Fig.\ \ref{fig:11-a}, the default setting wins in most cases.

\begin{comment}
\begin{figure*}
  \centering
  \subfigure[Precision]{
    \label{fig:11-a}
    \includegraphics[width=0.315\textwidth]{figures/precisionofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:11-b}
    \includegraphics[width=0.315\textwidth]{figures/recallofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:11-c}
    \includegraphics[width=0.315\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
  \caption{\sys{} Performance of Using Various Data Items for Modeling.}
  \label{fig:11}
  \vspace{-4ex}
\end{figure*}
\end{comment}

\begin{figure*}[tb!]
\vspace{-2ex}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
  \vspace{-4ex}
\end{figure*}

@@

%\noindent\textbf{Summary}. %From these experimental results we find the followings.
%(1) We design a novel method to extract users' explicit/implicit interests, and case studies show that our method is effective.
%(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
%
To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%. What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.

### 2017-12-24 DASFAA_2018/Gruba/07-rela.tex

In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basics, behavior and interest.

For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process, but uses the mined features as the input for user clustering and group based behavior modeling.

@@

The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
\cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
\cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.

>>>>

\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basics, behavior and interest.

For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14} and occupation \cite{IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process, but uses the mined features as the input for user clustering and group based behavior modeling.

@@

The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
\cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
\cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
Whereas our work \sys{} builds the \retg{} model for each user group, instead of a single model for all users or one model per user.

### 2017-12-24 DASFAA_2018/Gruba/08-conclu.tex

In this work, we have presented \sys{}, a system to model the \retg{} behavior of users in social media.
\sys{} departures from existing work by grouping users into clusters, during which features of basics, behavior and interests are extracted.
Specially, we have studied interest features from various perspectives, such as long-term/recent interests and explicit/implicit interests.
Finally, we have provided a performance evaluation of \sys{} by using real-world datasets to demonstrate the benefits of our system \sys{}.

>>>>

\par In this work, we have presented \sys{}, a system to model the \retg{} behavior of users in social media.
\sys{} departures from existing work by grouping users into clusters, during which features of basics, behavior and interests are extracted.
Specially, we have studied interest features from various perspectives, such as long-term/short-term interests and explicit/implicit interests.
Finally, we have provided a performance evaluation of \sys{} by using real-world datasets to demonstrate the benefits of our system \sys{}.
